Viral and Bacterial Communities of Colorectal Cancer

### 2017-06-19 doc/manuscript.Rmd
Forgot to push these too.

| ***Journal***: PNAS ([*Preparation Details*](http://www.pnas.org/site/authors/procedures.xhtml))
| ***Major Classification***: Biological Sciences
| ***Minor Classification***: Microbiology

@@

\* *Figures included for internal editing purposes*

@@

**Word Count**: 213 / 250

@@

**Word Count**: 111 / 120

@@

# Methods

@@

>>>>

| ***Major Classification***: Biological Sciences
| ***Minor Classification***: Microbiology

@@

@@

@@

@@

# Materials & Methods
This study was approved by the University of Michigan Institutional Review Board and all subjects provided informed consent. A detailed description of protocols used for sample collection, processing, and analysis is provided in SI Materials and Methods. All study sequences are available on the NCBI Sequence Read Archive under the BioProject ID `PRJNA389927`. All associated source code is available at the following GitHub repository:

https://github.com/SchlossLab/Hannigan_CRCVirome_PNAS_2017.

@@

# Supplemental Materials & Methods
